Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-07-06 manuscript/manuscript.qmd

For each selected RCT, a detailed protocol, pre-specifying key elements of the trial emulation, will be developed using the HARPER protocol template[@wang2022harmonized;@guidelinegeneral] and will be registered on ClinicalTrials.gov after review by an expert panel comprising clinicians and FDA reveiwers. Following the target trial emulation framework, we will provide an explicit description and rationale on how each element will be emulated including database selection, covariate measurement, operationalization of key eligibility criteria, study design, data analysis and causal contrasts of interest.[@hernan2022target; @hernan2016specifying] Since it is common that oncology RCTs update survival estimates periodically based on accrued follow-up time, the protocol will give a brief summary of each emulated RCT and specify which target OS estimates will be used for agreement metric evaluation (see @sec-agreement-metrics). All eligibility criteria will be extracted based on publications, publicly available protocols, and statistical analysis plans of the selected RCT.

>>>>

For each selected RCT, a detailed protocol, pre-specifying key elements of the trial emulation, will be developed using the HARPER protocol template[@wang2022harmonized; @guidelinegeneral] and will be registered on ClinicalTrials.gov after review by an expert panel comprising clinicians and FDA reveiwers. Following the target trial emulation framework, we will provide an explicit description and rationale on how each element will be emulated including database selection, covariate measurement, operationalization of key eligibility criteria, study design, data analysis and causal contrasts of interest.[@hernan2022target; @hernan2016specifying] Since it is common that oncology RCTs update survival estimates periodically based on accrued follow-up time, the protocol will give a brief summary of each emulated RCT and specify which target OS estimates will be used for agreement metric evaluation (see @sec-agreement-metrics). All eligibility criteria will be extracted based on publications, publicly available protocols, and statistical analysis plans of the selected RCT.
